### 2015-06-11 ApresentacoesArtigos/quali/quali.tex
adiantos na intro e estrutura

\section{Related work}

@@

\chapter{Chronogram and outline of finished and planed tasks}

% colocar comparativos aqui
\section{Documents}
\subsection{To be finished}

\subsubsection{Anthropological physics}
The study of human systems raises conceptual
and ethical issues that require anthropological considerations.
There are two immediate routes to this concepts:
\begin{itemize}
	\item What data should or can be used?
	\item Can one experiment in a network of humans? In which context?
\end{itemize}

@@

>>>>

\section{Literature review}
The field  of complex networks is relatively new ($\approx 25$ years)
and literature presents diverging definitions.
One definition that is having increasing acceptance
considers a complex network a ``large graph with non-trivial topological features''.
This definition is misleading in at least two points: there are networks of interest with trivial topological features, such as the paradigmatic Erdös-Rényi network and the lattice network~\cite{newman}. 
Second, it fails to deliver the fundamental message that the complex network is not an isolated mathematical graph structure. Complex networks of interest are real networks or idealized models for understanding them. Besides that, not only large graphs are of interest, but small graphs are very often used as toy examples and measured as extension of larger structures.
A definition, still far from perfect, but preferred in this work, is:
%``often large graphs considered in the physical
%or natural environment they reside''.
``often large and non-trivial graphs considered in,
or for the consideration of, 
the environment they reside''.
This definition resolves both issues.

Books in general present a common and powerful repertory for characterization of complex systems through graphs. Maybe most importantly are the arsenal of measures: degree, strength, betweenness centrality, clustering coefficient, etc.; the basic network paradigms: Erd\"os Rényi, geographical, small-world, scale-free; and the transdisciplinary approach to the environments that yield the networks. The literature on social network analysis,foe example, can often be understood as dealing with complex networks in human social systems.

A careful consideration of the books and articles read for this research
is given in Section~\ref{}.

@@

\chapter{Finished and planed tasks, chronogram}
% colocar comparativos aqui
\section{Documents}
\subsection{To be finished}
\subsubsection{Anthropological physics}
The study of human systems raises conceptual
and ethical issues that require anthropological considerations.
There are two immediate routes to this concepts:
\begin{itemize}
	\item What data should or can be used?
	\item Can one experiment in a network of humans? In which context?
\end{itemize}

@@

\section{Chronogram}
